Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-03 parts/def-ph.tex
typos

\modn{
\begin{remark}[Comparison with the Process Hitting]
  The Process Hitting framework
  previously introduced in~\cite{PMR10-TCSB}
  is a restriction of the AAN formalism;
  indeed, a Process Hitting model is an AAN so that
  $\forall h \in \PHh, 0 \leq \card{\hitter{h}} \leq 1$.
  However, the AANs defined in this paper have the same expressivity than
  the Process Hitting with classes of priorities, as previously
  introduced in~\cite{FPMR13-CS2Bio}.
  Indeed, in the Process Hitting with at least classes of priorities
  it is possible to use additional sorts, called “cooperative sorts”,
  in order to model the actions of any AAN that have more than one hitter.
\end{remark}
}

>>>>

\modn{
\begin{remark}[Comparison with the Process Hitting]
  The Process Hitting framework
  previously introduced in~\cite{PMR10-TCSB}
  is a restriction of the AAN formalism;
  indeed, a Process Hitting model is an AAN so that
  $\forall h \in \PHh, 0 \leq \card{\hitter{h}} \leq 1$.
  However, the AANs defined in this paper have the same expressivity than
  the Process Hitting with classes of priorities, as previously
  introduced in~\cite{FPMR13-CS2Bio}.
  Indeed, in the Process Hitting with at least 2 classes of priorities
  it is possible to use additional automata, called “cooperative sorts”,
  in order to model the actions of any AAN that have more than one hitter.
\end{remark}
}

### 2015-02-03 parts/sa.tex
typos

From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
\begin{lemma}
Given a state $s\in L$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
$\forall\delta\in\concr(\obj{a_i}{a_j})$,
$\exists\zeta\in\BS(\obj{a_i}{a_j})$ such that
$\exists \phi: \indexes{\zeta}\to\indexes{\delta}$
with
$\forall n,m\in\indexes{\zeta}, n<m \Leftrightarrow \phi(n)<\phi(m)$
and
$\forall n\in\indexes{\zeta}$, $\zeta_n = \delta_{\phi(n)}$.
\label{lem:bs-concr}
\end{lemma}

@@

  \modMF{%
  This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
  Indeed, the representation based on the Process Hitting that was proposed
  in this paper only allowed to represent “over-approximated” Boolean gates
  with the use of cooperative sorts.
  This especially did not allow to model the fact that $a_1$ and $b_1$ could not
  be activated in the same state, but only in successive states.
  Thus, when using Process Hitting, $c_1$ was indeed reachable,
  contrary to the behaviour expected from an accurate Boolean gate.
  }%

>>>>

From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
\begin{lemma}
Given a state $s\in \PHl$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
$\forall\delta\in\concr(\obj{a_i}{a_j})$,
$\exists\zeta\in\BS(\obj{a_i}{a_j})$ such that
$\exists \phi: \indexes{\zeta}\to\indexes{\delta}$
with
$\forall n,m\in\indexes{\zeta}, n<m \Leftrightarrow \phi(n)<\phi(m)$
and
$\forall n\in\indexes{\zeta}$, $\zeta_n = \delta_{\phi(n)}$.
\label{lem:bs-concr}
\end{lemma}

@@

  \modMF{%
  This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
  Indeed, the representation based on the Process Hitting that was proposed
  in this paper only allowed to represent “over-approximated” Boolean gates
  with the use of so-called cooperative sorts.
  This especially did not allow to model the fact that $a_1$ and $b_1$ could not
  be activated in the same state, but only in successive states.
  Thus, when using Process Hitting, $c_1$ was indeed reachable,
  contrary to the behaviour expected from an accurate Boolean gate.
  }%
